First of all, I would like to thank my supervisor, Professor Hussein Suleman, for giving me the opportunity to work with him; and for his encouragement, technical advice and support throughout my graduate studies. He read carefully early drafts of the manuscript, and his suggestions and proposed corrections contributed to the final form of this thesis. I am very grateful for this.

In addition, a number of individuals implicitly and explicitly contributed to this thesis in one way or the other. To these people, I would like to express my sincere thanks. In particular, I would like to thank Nicholas Wiltshire for facilitating access to the Spatial Archaeology Research Unit (SARU) Rock Art digital collection; Miles Robinson and Stuart Hammar for basing their ``Bonolo'' honours project on the Bleek and Lloyd case study collection; Kaitlyn Crawford, Marco Lawrence and Joanne Marston for basing their ``School of Rock Art'' honours project on the SARU Rock Art archaeological database case study collection; the University of Cape Town Computer Science Honours class of 2012 for taking part in the developer survey; and especially Kyle Williams for his willingness to help. 
%Thank you also goes to \href{http://www.89xradio.com}{89X radio} --the last mile was made the more possible by you guys!

%Furthermore, I would like to thank Michelle Wilmers for giving me the
%opportunity to be part of the Scholarly Communication in Africa Programme, and
%Niek De Greef from The Center for Curating the Archive. I learnt quite a lot
%working with them.

Furthermore, I would like to thank the Centre for Curating the Archive at the University of Cape Town and the Department of Archeology at the University of Cape Town for making available the digital collections that were used as case studies. I would also like to thank the Networked Digital Library of Thesis and Dissertation (NDLTD) for implicitly facilitating access to the dataset used in performance experiments through their support for open access to scholarship.

Finally, I would like to express my sincere gratitude to my family for their support during my long stay away from home.
%--Mom, Dad; those weekly, Sunday, late-afternoon, calls were a reality check and that really helped  me focus.